---
title: "Plots of the restaurants analysis"
output:
  pdf_document:
    toc: yes
    toc_depth: 4
    number_sections: yes
    fig_width: 7
    fig_height: 3
    fig_caption: yes
    df_print: kable
    highlight: tango
    latex_engine: xelatex
  html_document: default
header-includes:
    - \usepackage{setspace}\setstretch{1.1}
    - \usepackage{float}
    - \usepackage{booktabs}
geometry: margin=1in
fontsize: 11pt
fig_caption: yes
indent: false
---

\newpage

# Setup the enviroment

```{r,eval=F}
setwd("basicUtils/")
devtools::document()
devtools::install()
devtools::load_all()
setwd("..")
```


```{r, warning=F, comment=F, message=F}
library(gridExtra)
library(cowplot)
library(grid)
library(basicUtils)
library(tidyverse)
library(ggthemes)
```


```{r,  warning=F, comment=F, message=F}
to_knit = T
#levander blueSky greyGreen green purple grey red blueGrey yellow sparklingGreen orrange beige purple_smooth
l = getColors("greenbeige")
l
baseColor = l$baseColor
bgColor = l$darkColor
if (to_knit==T){
baseSize = 9
shape_size=2
annot_size =2
line_size=0.5
}else{
baseSize = 21
shape_size=5
annot_size=4
line_size=2
}
l$lightColor
highlightColor = l$highlightColor
baseShape = 7
highlightShape = 15
fontTheme = 'sans'
serror = function(x) sqrt(var(x,na.rm = T) / length(x))
bgColor = l$highlightColor
```


\newpage 

# Definition of necessary functions

## Formalizing labels

```{r}

update_model_names <- function(k1) {
  k1$model <- factor(k1$model)
  levels(k1$model)[levels(k1$model)=="svdbinary"]="SVD\n(implicit)"
  levels(k1$model)[levels(k1$model)=="svdtrinary"]="SVD\n(p-aware)"
  levels(k1$model)[levels(k1$model)=="svdtrinaryexplicit"]="SVD\n(explicit)"
  levels(k1$model)[levels(k1$model)=="explicit_SVD"]="SVD\n(explicit)"
  levels(k1$model)[levels(k1$model)=="cnn"]="CNN\n(implicit)"
  levels(k1$model)[levels(k1$model)=="lstm"]="LSTM"
  levels(k1$model)[levels(k1$model)=="svm"]="SVM"
  levels(k1$model)[levels(k1$model)=="xg"]="XGBoost"
  levels(k1$model)[levels(k1$model)=="trinary_SVD"]="SVD\n(p-aware)"
  levels(k1$model)[levels(k1$model)=="sahoo"]="HMM-CF\n(implicit)"
  levels(k1$model)[levels(k1$model)=="logit"]="Lgistic\nregression"
  levels(k1$model)[levels(k1$model)=="rf"]="Random\nforest"
  levels(k1$model)[levels(k1$model)=="hmm"]="HMM"
  levels(k1$model)[levels(k1$model)=="fb"]="Reputation\n(implicit)"
  return(k1)
}
```


## Getting general percentage improvement

```{r}
get_imprvement = function(d,algorithm){
  new_d = ((d$hmm - d[,algorithm])/d[,algorithm]) * 100
  return(new_d)
}
```

## Estimating regression lines and getting confidence intervals

```{r}
get_labels = function(r,level){ #regression labels
t = tibble()
avg = se = 1
for(model in unique(r$model)){
    r[r$model==model,] ->cur_r
    res = lm(avg ~ n,cur_r)
    from = confint(res, 'n', level = level)[1]
    to = confint(res, 'n', level = level)[2]
    intercept = res$coefficients[1]
    #position to print the conf-int
    yposition = ifelse(intercept > 1, 0.9 * intercept, 
            ifelse(intercept > 0, -20 * intercept, 2 * intercept))#intercept
    t %>% bind_rows(tibble(from,to,model,yposition,avg,se)) -> t
}
return(t)
}

```

## Generate a ranking performance plot

```{r}
get_ranking_performance_plot = function() {
get_focal_imprvs = function(algorithm){
  new_d = get_imprvement(d,algorithm) %>% bind_cols(d %>% select(prc,fold))
  new_d %>% rename(improvement = algorithm) %>% mutate(model = algorithm) %>% 
  group_by(model,prc) %>% summarise(avg=mean(improvement), 
                                      se = serror(improvement))-> new_d 
    return(new_d)
  }
d = read.csv(paste("../../data/evaluation_results/ranking_performance.csv", 
                   sep=""))
baselines = unique(d$algorithm)
baselines = baselines[baselines != 'hmm']
d %>% pivot_wider(names_from = algorithm, values_from=score)-> d
baselines %>% map_dfr(get_focal_imprvs) -> r
r %>%  update_model_names %>%  ggplot( aes(x = prc, y = avg, 
                          ymin = (avg - 1.645 * se), ymax = (avg + 1.645 * se),
                      color = baseColor, fill = '1')) +
    geom_col(alpha=0.4,size=line_size)+
    facet_wrap(~model, ncol = 6, scales = "free_y") +
    geom_errorbar(width = 0.3) +
    scale_color_manual(values = c(baseColor), name = "Improvement over") +
    scale_fill_manual(values = c(bgColor), name = "Improvement over") +
    xlab("Ranked cohort (p)") +
    scale_x_continuous(breaks = c(0.5,1),labels =c('Bottom 50%', 'Top 50%')) +
    geom_hline(yintercept = 0, linetype = "dashed") +
    geom_vline(xintercept = 0.5, linetype = "dashed", alpha = 0.4) +
    ylab(" Performance lift (%)") +
    theme_hc(base_size=baseSize)+
    theme(strip.background =element_rect(fill=alpha(bgColor,0.4)))+
    theme(legend.position = "none")+
  theme(axis.title = element_text())->p
  return(p)
}
```

## Generate an AUC-n plot

```{r}
get_auc_n_plot = function() {
  get_focal_imprvs = function(algorithm){
    new_d = get_imprvement(d,algorithm) %>% bind_cols(d %>% select(n,fold))
    new_d %>% rename(improvement = algorithm) %>% mutate(model = algorithm) %>%
    group_by(model,n) %>% summarise(avg=mean(improvement), 
                                    se = serror(improvement))-> new_d 
    return(new_d)
  }
d = read.csv("../../data/evaluation_results/auc_single_assessment.csv")
baselines = unique(d$algorithm)
baselines = baselines[baselines != 'hmm']
d %>% pivot_wider(names_from = algorithm, values_from=score)-> d
baselines %>% map_dfr(get_focal_imprvs) -> r
get_labels(r,level=0.9) %>% update_model_names ->t
r %>% update_model_names %>%  ggplot(aes(x = n, y = avg, 
                          ymin = (avg -1.645 * se), ymax = (avg + 1.645 * se),
                                         color = baseColor, shape = '1')) +
  geom_smooth(aes(fill = bgColor), method = 'lm', alpha = 0.4,size=line_size)+
  scale_color_manual(values = c(baseColor), name = "Improvement over") +
  scale_fill_manual(values = c(bgColor), name = "Improvement over") +
  scale_shape_manual(values = c(baseShape), name = "Improvement over") +
  xlab("") +
  geom_text(t, mapping = aes(x = 10, y =yposition, 
          group = model, 
          label = paste("Slope 90% CI: [", round(from, 2), ", ", 
                        round(to, 2), "]", sep = ""),     
          size = annot_size, color = baseColor),
          check_overlap = T,inherit.aes = FALSE, size=annot_size) +
  scale_x_continuous(breaks = c(1, 5,10, 15,20)) +
  facet_wrap(~model, ncol = 5,  scales = "free_y")+
  geom_hline(yintercept = 0, linetype = "dashed") +
  ylab("AUC Improvement (%)") +
  theme_hc(base_size=baseSize)+
    theme(strip.background =element_rect(fill=alpha(bgColor,0.4)))+
  theme(legend.position = "none")+
  theme(axis.title = element_text())->p
  return(p)
}
```


## Generate a within-opening performance plot

```{r}
get_within_opening_perf_plot <- function() {
  topN = 17 #median number of applications over 4 (55/4) 
            #-- top 25% of options within each opening.
  d <- read.csv(paste("../../data/evaluation_results/within_openings.csv",
                      sep = "")) %>% filter(n==topN)
get_focal_imprvs = function(algorithm){
    new_d = get_imprvement(d,algorithm) %>% bind_cols(d %>% select(fold))
    new_d %>% rename(improvement = algorithm) %>% mutate(model = algorithm) %>%
    group_by(model) %>% summarise(avg=mean(improvement), 
                                  se = serror(improvement))-> new_d 
    return(new_d)
  }
baselines = unique(d$algorithm)
baselines = baselines[baselines != 'hmm']
d %>% pivot_wider(names_from = algorithm, values_from=score)-> d
baselines %>% map_dfr(get_focal_imprvs) -> r
r %>% update_model_names %>% ggplot(aes(x = model, y = avg, 
                              ymin = avg - 1.645 * se, ymax = avg + 1.645 * se,
                                          color = '1', shape = '1')) +
  geom_point(size = shape_size) +
  geom_errorbar(width = 0.2) +
  ylab("Improvement (%)") +
  xlab(expression(paste(""))) +
  theme_hc(base_size=baseSize)+
    theme(strip.background =element_rect(fill=alpha(bgColor,0.4)))+
  scale_color_manual(values = c(baseColor, baseColor, baseColor)) +
  scale_shape_manual(name = "", values = c(baseShape, baseShape, baseShape)) +
  theme(legend.position = "none") +
  geom_abline(slope = 0, intercept = 0, linetype = 'dashed')+
  theme(axis.title = element_text())+
  facet_wrap(~"Within-task improvement of the HMM framework over alternative
             recommenders",strip.position = "top")
}
```


## Generate a basic AUC plot

```{r}
get_auc_plot<- function(inputfile) {
d = read_csv(paste("../../data/evaluation_results/",inputfile,sep="")) %>% 
  filter(n==0)
get_focal_imprvs = function(algorithm){
    new_d = get_imprvement(d,algorithm) %>% bind_cols(d %>% select(fold))
    new_d %>% rename(improvement = algorithm) %>% mutate(model = algorithm) %>% 
    group_by(model) %>% summarise(avg=mean(improvement), 
                                  se = serror(improvement))-> new_d 
    return(new_d)
}
baselines = unique(d$algorithm)
baselines = baselines[baselines != 'hmm']
d %>% select(fold,algorithm,score) %>%  pivot_wider(names_from = algorithm, 
                                                    values_from=score)->d 
baselines %>% map_dfr(get_focal_imprvs) -> r
r %>% update_model_names %>% ggplot(aes(x = model, y = avg, 
                                        ymin = avg - 1.645 * se,
                                        ymax = avg + 1.645 * se,
                      color = 'r', shape = 'r')) +
  geom_point(size = shape_size) +
  geom_errorbar(width = 0.2) +
  ylab("Improvement (%)") +
  xlab(expression(paste(""))) +
  geom_vline(xintercept = c(10.5), linetype = "dashed") +
  theme_hc(base_size=baseSize)+
    theme(strip.background =element_rect(fill=alpha(bgColor,0.4)))+
  scale_color_manual(values = c(baseColor, baseColor, baseColor)) +
  scale_shape_manual(name = "", values = c(baseShape, baseShape, baseShape)) +
  theme(legend.position = "none") +
  geom_abline(slope = 0, intercept = 0, linetype = 'dashed')+
  theme(axis.title = element_text())+
  facet_wrap(~"AUC improvement of the HMM framework over alternative recommenders",strip.position = "top")->p
return(p)
}
```


\newpage 

# Creating the paper's figures

## Figure 12: AUC comparison 


```{r,  warning=F, comment=F, message=F}
get_auc_plot('auc_single_assessment.csv') ->p
ggsave(file = 
    paste("../../../../../../Apps/Overleaf/gbu/ms/r2/figures/rest_auc.pdf", sep = ""), 
    width = 14, height = 5, dpi = 300)
p
```


\newpage 
## Figure 13: AUC-n comparison 

```{r,  warning=F, comment=F, message=F}
p = get_auc_n_plot()
ggsave(file = 
        paste("../../../../../../Apps/Overleaf/gbu/ms/r2/figures/rest_aucn.pdf", 
                    sep = ""), width = 16, height = 5, dpi = 300)
p
```



## Figure 14: Ranking performance


```{r,  warning=F, comment=F, message=F}
p = get_ranking_performance_plot()
ggsave(file = 
  paste("../../../../../../Apps/Overleaf/gbu/ms/r2/figures/rest_ranking_performance.pdf", 
  sep = ""), width = 16, height = 5, dpi = 300)
p
```



## Figure 15: Performance within openings



```{r,  warning=F, comment=F, message=F}
p = get_within_opening_perf_plot()
ggsave(file = 
paste("../../../../../../Apps/Overleaf/gbu/ms/r2/figures/rest_withinOpenings.pdf",
          sep = ""), 
    width = 14, height = 5, dpi = 300)
p
```

\newpage
## Figure 16: AUC comparison -- many assessment




```{r,  warning=F, comment=F, message=F}
get_auc_plot('auc_many_assessment.csv')->p
ggsave(file = 
paste("../../../../../../Apps/Overleaf/gbu/ms/r2/figures/rest_many_assessment.pdf", 
        sep = ""), 
  width = 14, height = 5, dpi = 300)
p
```






